Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-04 docs/ms.tex
Update ms.tex

\subsection{Bias Test}

We test the systematical bias of our estimator.(Here the estimator
is the max-marginalized likelihood estimator?) We plot $g_{1}-g_{1}^{true}$
VS $g_{1}^{true}$ ,and put on an error bar which equals standard
deviation of marginalized likehood functon $p(Data|g_{1})$ ,and use
a linear fit to determin the m,c value and their standard deviations.

>>>>

\subsection{Bias Test}
In this section,we measured the levels of possible systemmatical
bias of this Hierachical inference method.
Following Heymans et al. (2006), we quantify the systematic bias in
in terms of the multiplicative error m and additive error c on the
true shear $g^{true}$ 
\begin{equation}
\hat{g_{i}}-g_{i}^{true}=m_{i}g_{i}^{true}+c_{i}
\end{equation}

The accuracy of Weak Lensing survey depends on both galaxy shape measurement
and shear inference .In this paper our main concern is how to infere
shear in a HB method instead off traditional averaging method and
it does not involve the shape measurement part .Therefore we assume
we have perfect galaxies ellipticity measurement,and all the possible
inaccuracy is due to this HB shear inference method.

We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
sets as described above.Each data set has 64 patches and 8{*}64 galaxies,and
the true P($\epsilon$) is Beta(2.8,2.8) .For both Beta function model
and step funtion model we then determin the best fitted parameters
m and c of fomula (15).Figure 9 shows an example of step funtion model
with prior prefator $\xi=3$.The results of the systematical bias
analysis are tabulated in table 1.
